\documentclass[11pt]{article}
\sloppy
\usepackage{xcolor}
\usepackage{scrlayer-scrpage}

\newcommand{\MyName}{P. Lerdkijrachapong}

\usepackage{blindtext}

\clearscrheadfoot
\rohead{\MyName}
\lehead{\today}

\chead{What the PM election today?}
\lohead{\today}
\rehead{\MyName}    
\cefoot{\thepage}


\begin{document}
Since the 19th of August 2025, Thailand's politic has been an interesting watchlist, as \textit{Ms. Paetongtarn Shinawatra} has been removed from the status of prime minister following the ruling of the Constitutional Court of Thailand; and for the first time in multiple years, Thailand is now facing a new age of politic.

To understand the weight of the situation, the \textit{Shinawatra} family has been deeply rooted in Thai's politic since 2001, with \textit{Mr. Thaksin Shinawatra} being the first in \textit{Shinawatra} lineage to become prime minister of Thailand. Since then, there has been \textbf{4} prime minister from his lineage, and his political party. \textbf{However}, the removal of \textit{Ms. Paetongtarn Shinawatra}\textemdash the \textbf{4th} successor of \textit{Shinawatra} lineage\textemdash the distrust of \textit{Pheu Thai Party} from public, marks the end of ``\textbf{\textit{Shinawatra's Political Dynasty}}".

While it's impressive that the end of this lineage is the result of a mistake in diplomacy technique mixes with a spark in public opinion. The end of \textit{Shinawatra's Political Dynasty} will create a vacuum in Thai's political system; and with no ``big" player as powerful as  \textit{Mr. Thaksin Shinawatra} in the system, being in Thai politic will be equivalent to being stranded in the red ocean, surrounded by political parties that want power.

It can be argued that the new age of Thailand's politic is as impressive as it will be disappointing. To elaborate, it is surely impressive that Thailand's political parties are able to gather member of parliament, come up with a new plan to suffice the removal of \textit{Ms. Paetongtarn Shinawatra}, and vote for a new prime minister, on the 5th of September 2025, within a week after the ruling of the Constitutional Court. However, from the past of Thailand's situation, from a big problem as corruption, to small problem as mistake in fundamental policies; we can most certainly acknowledge that every of current Thailand's political parties are not worthy of being the leader, not even the newest prime minister of Thailand \textit{Mr. Anutin Charnvirakul} and his party ``\textit{Bhumjaithai Party}".

The convergence of the ending of \textit{Shinawatra's Political Dynasty}, the starting of a new period of Thailand's political vacuum gap, and the incompetence of Thailand's political parties, emphasize the question that every Thai citizen have asked since forever:

\begin{center}
	\textbf{Who can we really trust, and ensure our country's future with?}
\end{center}
\end{document}
